---
title: "p8105_hw_ef2721"
author: "Erfan Faridmoayer"
output: github_document
date: "Fall 2022"
---


```{r}
# Before starting the code, introduced two libraries, and made sure code chuncks are visible.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gtsummary)
```


## Problem 1

This is a code chunk for importing the data about penguins.

```{r}
data("penguins", package = "palmerpenguins")
f = penguins$flipper_length_mm
```


```{r}
# I first wanted to change the column names for table presentation
peng_df = penguins

colnames(peng_df)[colnames(peng_df) == "species"] = "Species"
colnames(peng_df)[colnames(peng_df) == "island"] = "Island"
colnames(peng_df)[colnames(peng_df) == "bill_length_mm"] = "Bill Length (mm)"
colnames(peng_df)[colnames(peng_df) == "bill_depth_mm"] = "Bill Depth (mm)"
colnames(peng_df)[colnames(peng_df) == "flipper_length_mm"] = "Flipper Length (mm)"
colnames(peng_df)[colnames(peng_df) == "body_mass_g"] = "Body Mass (g)"
colnames(peng_df)[colnames(peng_df) == "sex"] = "Sex"
colnames(peng_df)[colnames(peng_df) == "year"] = "Year"

# Used the gtsummary library to showcase the dataset description in a table, with statistical variables
tab1 = tbl_summary(peng_df, by = Island, missing ="no")
tab1
```

The table above is a desciption of the dataset based on the penguins' islands.

Here is some more info about our dataset:

* This dataset includes information about penguins' species, island of origin, gender, bill-length, bill-depth, flipper length, mass, and year of data collection.
* There are a total of **`r nrow(penguins)`** penguins in this collection, with **`r ncol(penguins)`** collected variables. 
* The mean flipper length for these penguins was **`r mean(f, na.rm=TRUE)`**.




